Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion

### 2018-09-26 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update paper and add voting data

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris Cochrane for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%d %B %Y')`; **comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "Government policy is partly driven by the topics that are discussed in parliament. Conversely, those same topics can indicate a government's priorities. But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary debate. In this paper, we systematically analyse how parliamentary debate has changed in response to different types of events in Australian history. We compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records. We use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time. We then examine the effect of various events using a discrete choice model. We find that: 1) changes of government are associated with topic changes only when there is also a change of the party in power; and 2) economic events, such as financial crises, have significant and persistent effects. Our findings have implications for how we think about the longer-term trajectory of government policy as the media cycle becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

Australian Hansard records have been analysed for various purposes, usually at smaller-scale. For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. And @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.

Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release. There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records publicly available across the state and federal parliaments (Table 1) **[UPDATE NUMBERING]**. As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in the Appendix.

[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website (http://historichansard.net/) that can be used to explore Commonwealth Hansard records from 1901 to 1980. Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through today from Open Australia’s website.

@@

[^seeMyScripts]: An example of the workflow and some reduced-detail scripts are provided in the Appendix. The full set of scripts are available on request.

**[ADD PICTURE OF HANSARD RECORD AND THE SUBSEQUENT TEXT RECORD?]**

@@

Text usually needs to be pre-processed before topic models can be used. The specific steps that we take are to remove numbers and punctuation and to change all the words to lower case. Then the sentences are deconstructed and each word considered individually. In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.

@@

[^seeMyAdditionalData]: An example of the additional information is provided in the Appendix. The datasets are available on request.

# Model
The main models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and a discrete choice model as implemented by the \texttt{XXXX} R package of **XYZ**. In theory we could have directly used the text as an input to the discrete choice model, but this is intractable due to computer memory and storage constraints. Instead, in a similar way to @MuellerRauh2018, we use the topics that the text is about as an input to another model, which in our case is a discrete choice model.

@@

## Latent Dirichlet Allocation
Although more- or less-fine levels of analysis are possible, but here we are primarily interested in considering a day's topics. This means that each day's Hansard record needs to be classified by its topics. Sometimes Hansard records includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods. One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent, for instance as implemented by the R package 'topicmodels' by @Grun2011.

The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics. A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions. The topics are not specified *ex ante*; they are an outcome of the method. In this sense, this approach can be considered unsupervised statistical learning. Terms are not necessarily unique to a particular topic, and a document could be about more than one topic. This provides more flexibility than other approaches such as a strict word count method. The goal is to have the words found in each day's Hansard group themselves to define topics.

@@

## Structural Topic Model
The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it includes additional information about documents. For instance, in general we usually have some information about the author and date of a document. In the case of Hansard, we know who was speaking and the date. STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content. That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.

The STM is set-up to most easily include metadata to do with prevalence and content. Prevalence relates to the topic proportions in each document. For instance, we expect that topics related to the reasons for Federation such as tariffs and trade should be more prevalent in those earlier years than later. Similarly, we may expect topics to do with terrorism to be more prevalent in recent years than in earlier ones. Content relates to the words that make up each topic. For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.

Again, the assumed process that generates the documents is the key aspect as this will be reversed to estimate the topics. The document generation process of @Blei2003latent discussed earlier, is only slightly modified by @RobertsStewartAiroldi2016 for the STM:

1. The proportion of a document dedicated to a topic is drawn "from a logistic-normal generalised linear model based on a vector of document covariates $X_d$":
$$\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \sigma)$$
"where $X_d$ is a 1-by-p vector, $\gamma$ is a p-by-K - 1 matrix of coefficients and $\sigma$ is K-1 by K-1 covariance matrix." **THIS IS ALL QUOTES. NEED TO REWRITE.**
2. **THIS IS ALL QUOTES. NEED TO REWRITE.** Given a document-level content covariate $y_d$, form the document-specific distribution over words representing each topic ($k$) using the baseline word distribution $m$, the topic specific deviation, $\kappa_k^{(t)}$, the covariate group deviation, $\kappa_{y_d}^{(c)}$, and the interaction between the two, $\kappa_{y_{d}k}^{(i)}$:
$$\beta_{d,k}\sim exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) $$

HERE

1. There are  For each topic, decide the terms that the topic uses by randomly drawing distributions over the terms. The distribution over the terms for the $k$th topic is $\beta_k$. Typically a topic would be a small number of terms and so the Dirichlet distribution with hyperparameter $0<\eta<1$ is used: $\beta_k \sim \mbox{Dirichlet}(\eta)$.[^Dirichletfootnote] Strictly, $\eta$ is actually a vector of hyperparameters, one for each $K$, but in practice they all tend to be the same value.

STM can be implented using the stm R package of @RobertsStewartAiroldiRPackage.

@@

<!-- ![alt text](here::here(/outputs/figures/all_topics_usable.png)) -->

@@

### Considering events
We consider the effect of political, economic, and other events on Australian parliamentary discussion. Political events are those related to a change of government or an election (Tables \@ref(tab:governments) and \@ref(tab:elections)). Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or the Great Recession (Table \@ref(tab:economicevents)). Other events are those such as the 9/11 attacks, or the Bali Bombing (Table \@ref(tab:otherevents)). The list of events that we consider is detailed in .

@@

## External events
>*Events, dear boy, events.* Attributed to Harold Macmillan.

@@

@@

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris Cochrane for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%d %B %Y')`; **comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "Government policy is partly driven by parliamentary discussion. Conversely, that same discussion can indicate a government's priorities. But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary discussion. In this paper, we systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records. We use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time. We then examine the effect of various events using a discrete choice model. We find that: 1) changes of government are associated with topic changes only when there is also a change of the party in power; and 2) economic events, such as financial crises, have significant and persistent effects. Our findings have implications for how we think about the longer-term trajectory of government policy as the media cycle becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

Australian Hansard records have been analysed for various purposes. For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. And @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.

Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release. An example of what a page of Hansard looks like is included in Appendix **[ADD NUMBERING]**. There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records publicly available across the state and federal parliaments (Table 1) **[UPDATE NUMBERING]**. As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in Appendix **[ADD NUMBERING]**.

[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website (historichansard.net/) that can be used to explore Commonwealth Hansard records from 1901 to 1980. Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through to today from Open Australia’s website. The records can also be downloaded from the Australian Hansard website.

@@

[^seeMyScripts]: An example of the workflow and some reduced-detail scripts are provided in Appendix **[ADD NUMBERING]**. The full set of scripts are available on request.

@@

Text usually needs to be pre-processed before topic models can be used. The specific steps that we take are to remove numbers and punctuation and to change all the words to lower case. Then the sentences are deconstructed and each word considered individually. In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016. **NEED TO bundle_ngrams i.e. olive oil should be olive_oil, not considered separately.**

@@

[^seeMyAdditionalData]: An example of the additional information is provided in Appendix **[ADD NUMBERING]**. The datasets are available on request.

# Model
The main models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and a discrete choice model as implemented by the \texttt{XXXX} R package of **XYZ**. In theory we could have directly used the text as an input to the discrete choice model, but this quickly becomes intractable due to computer memory and storage constraints. Instead, in a similar way to @MuellerRauh2018, we use the topics that the text is about as an input to another model, which in our case is a discrete choice model. In Appendix **[ADD NUMBERING]**, we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.

@@

## Latent Dirichlet Allocation
Although more- or less-fine levels of analysis are possible, but here we are primarily interested in considering a day's topics. This means that each day's Hansard record needs to be classified by its topics. Sometimes Hansard records includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods. One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent, for instance as implemented by the R \texttt{topicmodels} package of @Grun2011.

The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics. A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions. The topics are not specified *ex ante*; they are an outcome of the method. In this sense, this approach can be considered unsupervised machine learning. Terms are not necessarily unique to a particular topic, and a document could be about more than one topic. This provides more flexibility than other approaches such as a strict word count method. The goal is to have the words found in each day's Hansard group themselves to define topics.

@@

## Structural Topic Model
The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it considers more than just a document's content when constructing topics. For instance, we generally have some information about the author and the date that a document was created. In the case of Hansard, we know who was speaking and the date they spoke. STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content. That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.

The STM is set-up to most easily include metadata to do with prevalence and content. Prevalence relates to the topic proportions in each document. For instance, we expect that topics related to the reasons for Federation, such as tariffs and trade, should be more prevalent in those earlier years than later. Similarly, we may expect topics to do with terrorism to be more prevalent in recent years. Content relates to the words that make up each topic. For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.

Again, the assumed process that generates the documents is the key aspect as this will be reversed to estimate the topics. The document generation process of @Blei2003latent discussed earlier, is slightly modified by @RobertsStewartAiroldi2016 for the STM:

**THIS NEEDS WORK START**

1. The proportion of a document dedicated to a topic, stored in the vector $\theta_d$, is drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a document covariates, $X_d$, following @RobertsStewartTingley2018:
$$\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
"where $X_d$ is a 1-by-p vector, $\gamma$ is a p-by-K - 1 matrix of coefficients and $\sigma$ is K-1 by K-1 covariance matrix." This is in contrast to the Dirichlet distribution that characterises LDA.
2. **THIS IS ALL QUOTES. NEED TO REWRITE.** Given a document-level content covariate $y_d$, form the document-specific distribution over words representing each topic ($k$) using the baseline word distribution $m$, the topic specific deviation, $\kappa_k^{(t)}$, the covariate group deviation, $\kappa_{y_d}^{(c)}$, and the interaction between the two, $\kappa_{y_{d}k}^{(i)}$:
$$\beta_{d,k}\propto exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) $$

**THIS NEEDS WORK END**

We implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage. We consider both topic prevalence and content to be functions of time. The choice of how many topics to use in the model is a situation-specific compromise. We use standard diagnostic techniques to decide on 80 topics, and more detail on this process is available in Appendix **[ADD NUMBERING]**.

One way to summarise the results of the topic model is to **????**

@@

@@

### Considering events
We consider the effect of political, economic, and other events on Australian parliamentary discussion. Political events are those related to a change of government or an election. Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or the Great Recession. Other events are those such as the 9/11 attacks, or the Bali Bombing. The full list of events that we consider is detailed in Appendix **[ADD NUMBERING]**. We consider events in two ways. The first is in the change in the word usage before and after events and the second is in changes in the topics.

Differences in word usage can be evaluated using the term frequency-inverse document frequency (tf-idf) measure. It will be higher for words that are rarely used across all documents, but commonly used in a document. For instance, in Australian parliamentary text records 'the' is commonly used in many documents and so the fact that it is used in any particular document is not usual. However, 'aboriginal' is less common across, and so if it was especially prevelant in a particular document that may distinguish that document.

When we consider events using tf-idf, we gather terms from more than one day. We define groups of days that are roughly analogous to sitting periods. If there is more than a week between a day then we define a new group, otherwise the day is in the existing group. We use various measures **(Text2vec R package has some? or some other package)** to define a baseline measure of how different each group is, and then test for whether groups separated by our events are significantly different to this baseline.

Changes in topics also help define how ...

@@

## Other events
>*Events, dear boy, events.* Attributed to Harold Macmillan.

@@

## Example page

```{r, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/example_hansard_page.png"))
```

@@

## Events

## Choosing number of topics

Add the graphs and procedures.

## word2vec alternative
An alternative approach that follows @Taddy2015.
